\pkg{RProtoBuf}: Efficient Cross-Language Data Serialization in \proglang{R}

### 2014-11-25 papers/jss/article.Rnw
Improve example in section 7 using some of the specific advantages suggested by referee #2 and point out why we've given the user a simplified example and how it differs from the real MapReduce context where this would be more useful.
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/rprotobuf@908 edb9625f-4e0d-4859-8d74-9fd3b1da38cb

This HistogramState message type is designed to be helpful if some of
the Map or Reduce tasks are written in \proglang{R}, or if those components are
written in other languages and only the resulting output histograms
need to be manipulated in \proglang{R}.  For example, to create HistogramState
messages in Python for later consumption by \proglang{R}, we first compile the 
\code{histogram.proto} descriptor into a python module using the
\code{protoc} compiler:

@@

One of the authors has used this design pattern with large-scale \proglang{C++}
MapReduces over very large data sets to write out histogram protocol
buffers for several large-scale studies of distributed storage systems
\citep{sciencecloud,janus}.

>>>>

This HistogramState message type is designed to be helpful if some of
the Map or Reduce tasks are written in \proglang{R}, or if those components are
written in other languages and only the resulting output histograms
need to be manipulated in \proglang{R}.

\subsection*{A trivial single-machine example for Python to R serialization}

To create HistogramState
messages in Python for later consumption by \proglang{R}, we first compile the 
\code{histogram.proto} descriptor into a python module using the
\code{protoc} compiler:

@@

This simple example uses a constant histogram generated in
\proglang{Python} to illustrate the serialization concepts without
requiring the reader to be familiar with the interface of any
particular MapReduce implementation.  In practice, using Protocol
Buffers to pass histograms between another programming language and R
would provide a much greater benefit in a distributed context.
For example, a first-class data type to represent histograms would
prevent individual histograms from being split up and would allow the
use of combiners on Map workers to process large data sets more
efficiently than simply passing around lists of counts and buckets.

One of the authors has used this design pattern with \proglang{C++}
MapReduces over very large data sets to write out histogram protocol
buffers for several large-scale studies of distributed storage systems
\citep{sciencecloud,janus}.
